---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ReX 
Reliability Explorer (ReX) - command line version

<!-- badges: start -->
[![R-CMD-check](https://github.com/TingsterX/ReX/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TingsterX/ReX/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**ReX (Reliability Explorer)** is a R toolbox for calculating reliability and mapping individual variations to facilitate the assessment of reliability and reproducibility in neuroscience and psychology. This toolbox provides two modules.

- Reliability Calculation module. This module implements parametric and nonparametric methods for univariate and multivariate reliability calculation including Intraclass correlation (ICC), distance-based ICC (dbICC), Image Intraclass Correlation Coefficient (I2C2), discriminability, and identification rate (i.e. fingerprinting). The results will be presented in a two-dimensional individual variation space (x-axis: within-individual variation, y-axis: between-individual variation) to facilitate understanding of individual difference and its relation to reliability assessment. The discriminability of each observation can be used to inspect your data and results. It will help to detect (1) which variable of interest has low reliablity, (2) which observation is a potential outliers.

- Individual Comparison module. This module provides plotting function to visualize your results in the two-dimensional individual variation space. For the paired comparison, ReX can calculate the gradient flow map provides the normalized change of the within- and between-individual variation as compared to the most efficient direction for improving ICC, which helps to guide optimization efforts for measurement of individual differences. 

See Shiny App version: https://github.com/TingsterX/Reliability_Explorer

## Installation

You can install the development version of ReX from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TingsterX/ReX")
```

## Dependency packages
dplyr, lme4, ggplot2, RColorBrewer, scales, stats, reshape2, colorspace, [I2C2](https://github.com/neuroconductor/I2C2)
``` r
devtools::install_github("muschellij2/I2C2")
```

## Example - Reliability Calculation module

This is a basic example which shows you how to calculate different types of reliability

```{r example_data}
library(ReX)
# demo data is included in ReX
head(demo_brain_trt[,1:8])
```

In this example, we only illustrate 20 dependent variables from the demo data here
```{r}
data <- as.matrix(demo_brain_trt[,5:24])
subID <- as.matrix(demo_brain_trt[,"subID"])        
session <- as.matrix(demo_brain_trt[,"visit"])         
cov <- as.matrix(demo_brain_trt[,c("age", "gender")])
```

#### Univariable Reliability - Intraclass Correlation (ICC) and variation field map
```{r ICC_exmaple}
# Calculate the univariable Reliability: Demonstrate One-way Random Model based ICC
df_icc <- data.frame(lme_ICC_1wayR(data, subID, session, cov))
head(df_icc)
# The within- and between-individual variation map
rex_plot.var.field(df_icc, size.point = 4,  alpha.density = 0.3, color.point.fill = "red", color="red")
```

#### Univariable Reliability - Discriminability
```{r discriminability}
# Calculate the univariable Reliability Discriminability
Discr_list <- discriminability_wraper(data, subID, session, all_discr.return=TRUE)
# Discriminability for each dependent variable
head(Discr_list$Discr)
# Discriminability for each observation and dependent variable
head(Discr_list$DiscrSub[1:6,1:6])
# Inspect the Discriminability for each observation and dependent variable
rex_plot.discri_matrix(Discr_list$DiscrSub[,-c(1,2)], subID, session)
```


#### Univariable Reliability - Identification Rate (Fingerprinting)
```{r IdentificationRate}
iRate_list <- fingerprinting_wraper(data, subID, session, method.dist = 'euclidean')
head(iRate_list$FP)
```


#### Multivariable reliability (reliability for all dependent variables together)
```{r multivariable_reliability}
# All multivariable reliability are based on the distance matrix
Dmax <- dist(data, method = "euclidean")

# I2C2
calc_i2c2(Dmax, subID, as.matrix(session))

# dbICC
calc_dbICC(Dmax, subID)

# discriminability
calc_discriminability(Dmax, subID)

# identification rate (fingerprinting)
calc_fingerprinting(Dmax, subID)

# plot the distance space (red shade: discriminated observations, red dot: identified observation)
dFM.df <- distance_field_map.df(Dmax, subID)
rex_plot.distance_field_map(dFM.df, point.size = 2)
```

# Example - Individual Comparison module
Demo data included in ReX: reliability and variation of brain connectivity preprocessed with and without global signal regression (GSR).
```{r}
# 62 observations includes 31 subjects and 2 visits per subject
df_baseline <- demo_icc_noGSR
df_target <- demo_icc_GSR
df_paired <- cbind(df_baseline, df_target)
# calculate the normalized changes of variation - gradient flow 
df_VarPairedComp <- icc_gradient_flow(df_target[,"sigma2_w"], df_target[,"sigma2_b"], df_baseline[,"sigma2_w"], df_baseline[,"sigma2_b"])
df_VarPairedComp$contrast <- "GSR - noGSR"
rownames(df_VarPairedComp) <- df_paired$X
head(df_VarPairedComp)
```

#### Change of the variation
Change of the within- and between-individual variation: target (GSR) vs baseline (noGSR)
```{r}
rex_plot.var.change(df_VarPairedComp)
```

#### Normalized change of the variation - gradient flow
Normalized (relative) change of the within- and between-individual variation: target (GSR) vs baseline (noGSR)
```{r}
rex_plot.icc.gradient.norm(df_VarPairedComp)
# Hisgotram of normalized change of the variation - gradient flow: target vs baseline
rex_plot.icc.gradient.hist(df_VarPairedComp)
```
