---
title: "demo_rex_comp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo_rex_comp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Compare the reliability and variations

load in R packages: ReX, dplyr 
```{r setup}
library(ReX)
library(dplyr)
```

**Example data:**: reliability and variation of brain connectivity preprocessed with global signal regression (GSR) and without.
see ?ReX::demo_icc_GSR and ?ReX::demo_icc_noGSR
```{r load_data}

# 62 observations includes 31 subjects and 2 visits per subject
df_baseline <- demo_icc_noGSR
df_target <- demo_icc_GSR
df_paired <- cbind(df_baseline, df_target)

df_VarPairedComp <- icc_gradient_flow(df_target[,"sigma2_w"], df_target[,"sigma2_b"], df_baseline[,"sigma2_w"], df_baseline[,"sigma2_b"])
df_VarPairedComp$contrast <- "GSR - noGSR"
rownames(df_VarPairedComp) <- df_paired$X

head(df_VarPairedComp)
```

### Change of the variation: target vs baseline
```{r}
rex_plot.var.change(df_VarPairedComp)
```


### Normalized (relative) change of the variation - gradient flow: target vs baseline
```{r}
rex_plot.icc.gradient.norm(df_VarPairedComp)
```

### Hisgotram of normalized (relative) change of the variation - gradient flow: target vs baseline
```{r}
rex_plot.icc.gradient.hist(df_VarPairedComp)
```
