---
title: "demo_rex_calc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo_rex_calc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Reliability and variation analysis

load in R packages: ReX, dplyr 
```{r setup}
library(ReX)
library(dplyr)
```

For illustration, we only take 10 columns from the demo data as dependent variables. Check out the demo data, see ?ReX::demo_brain_trt
```{r load_demo_data}
# 62 observations includes 31 subjects and 2 visits per subject
data <- as.matrix(demo_brain_trt[,5:14])
subID <- as.matrix(demo_brain_trt %>% select("subID"))        
session <- as.matrix(demo_brain_trt %>% select("visit"))         
# age, gender as covariance 
cov <- as.matrix(demo_brain_trt %>% select("age", "gender"))
head(demo_brain_trt[1:5,1:8])
```

### Univariate reliability (reliability for each dependent variable separately)
**Intraclass Correlation (ICC) model** will also estimate the inter- and intra-indivisual variations
Note: a singular fit might occur when a random effect is estimated very close to zero or the collinearity is found in fixed effects. 
Here, the demo data is a test-retest dataset
```{r ICC_calculation}
# One-way Random Model
icc1 <- lme_ICC_1wayR(data, subID, session, cov)
icc1
# Two-way Random Model
icc2 <- lme_ICC_2wayR(data, subID, session, cov)
icc2
# Two-way Mixed Model
icc3 <- lme_ICC_2wayM(data, subID, session, cov)
icc3
```
```{r}
df_icc1 <- data.frame(icc1)
# Default plotting configuration
rex_plot.var.field(df_icc1, size.point = 4,  alpha.density = 0.3, color.point.fill = "red", color="red")
```


```{r discriminability}
# Univariable Discriminability
Discr_list <- discriminability_wraper(data, subID, session, all_discr.return=TRUE)
# Discriminability for each dependent variable
Discr_list$Discr
# Discriminability for each observation and dependent variable
head(Discr_list$DiscrSub)
# Inspect the data
rex_plot.discri_matrix(Discr_list$DiscrSub[,-c(1,2)], subID, session)
```
```{r IdentificationRate}
# Univariable identification rate
iRate_list <- fingerprinting_wraper(data, subID, session, method.dist = 'euclidean')
# Identification Rate (fingerprinting) for each dependent variable
iRate_list
```

### Multivariable reliability (reliability for all dependent variables together)
```{r identification_rate}
# All multivariable reliability are based on the distance matrix
Dmax <- dist(data, method = "euclidean")

# I2C2
calc_i2c2(Dmax, subID, as.matrix(session))

# dbICC
calc_dbICC(Dmax, subID)

# discriminability
calc_discriminability(Dmax, subID)

# identification rate (fingerprinting)
calc_fingerprinting(Dmax, subID)

# plot the distance space (red shade: discriminated observations, red dot: identified observation)
dFM.df <- distance_field_map.df(Dmax, subID)
rex_plot.distance_field_map(dFM.df, point.size = 2)
```
